Policy Implications of Coupled Economic and Ecological Dynamics in Aquatic Systems

### 2022-11-17 03_marlin_paper.qmd
updating makefile instructions

<!-- Our MPA optimization algorithm seems to create an MPA network that -->
<!-- maximizes an objective function, given by -->

<!-- $$ -->
<!-- obj_p = \Phi \times scale(\sum_f^F \boldsymbol{\phi_{f,p}}) + (1 - \Phi)  scale(\boldsymbol{\sum_s^S\frac{ssb_s}{ssb0_{s,p}}}) -->
<!-- $$ {#eq-obj} -->

<!-- Where *scale* rescales the values to be between 0 and 1 such that the -->
<!-- weight parameter is comparable between vectors. The algorithm works by -->
<!-- first assigning every patch in the system to an MPA. For the first -->
<!-- round, the algorithm then calculates the equilibrium objective function -->
<!-- value resulting from sequentially removing each individual patch from -->
<!-- the MPA network. The cell whose removal from the MPA produces the -->
<!-- highest objective function value is then removed from the MPA network, -->
<!-- and the marginal value of the objective function each of the remaining -->
<!-- cells from the last steps are then stored. For the next steps, we -->
<!-- sampled 25% of the remaining MPA cells with probability proportional to -->
<!-- their marginal contribution to the objective function in the prior -->
<!-- iteration, selecting the cell whose removal produces the highest total -->
<!-- objective function as the cell to remove from the network, and updating -->
<!-- the marginal value of the sampled-but-not-selected cells. This in -->
<!-- essence is a sampling-importance-resampling algorithm. The algorithm -->
<!-- continues until no more cells are left in the MPA. This then provides -->
<!-- for a given objective weighting value $\Phi$ the near-optimal MPA -->
<!-- network at every MPA size from 0 to 100%. We say "near" as they is some -->
<!-- path dependency here, in that for example the network that maximizes the -->
<!-- objective function with 40% of the MPAs does not necessarily contain the -->
<!-- optimal network at 30%. However, the reversed nature of the algorithm, -->
<!-- starting at 100% MPA coverage and working better, produces a more stable -->
<!-- network with regards to this problem than starting at 0% and growing to -->
<!-- 100%. -->

@@

```{r}
#| label: fig-coral-results
#| fig-cap: "Frontier in conservation and yield outcomes under different MPA design strategies (A) for coral reef case study. Change in yield for each fleet (B) and depltion per species (C) as a function of MPA size and MPA design strategy () for coral reef case study."
#| fig-height: 4
#| fig-width: 6

coral_mpa_experiements$mpas <- map(coral_mpa_experiements$results, "mpa")

coral_mpa_experiements$obj <- map(coral_mpa_experiements$results, "obj")

coral_results <- coral_mpa_experiements %>%
  unnest(cols = obj)

@@

In this paper we have documented the core system of equations underlying
`marlin`, and demonstrated how this framework can be used to support
efforts such as MPA planning. The variation in both the magnitude and
distribution of costs and benefits stemming from alternative design
choices and states of nature shown in our results demonstrates the value
in our method. Beyond the current examples, we envision `marlin` being
applicable to research on dynamic ocean management, range shifts,
management strategy evaluation, policy interactions, and spatial stock
assessment. Future iterations of the model may include life history
modules for a broader range of species types such as marine mammals, sea
birds, and sea turtles.

>>>>

<!-- Our MPA optimization algorithm seems to create an MPA network that -->

<!-- maximizes an objective function, given by -->

<!-- $$ -->

<!-- obj_p = \Phi \times scale(\sum_f^F \boldsymbol{\phi_{f,p}}) + (1 - \Phi)  scale(\boldsymbol{\sum_s^S\frac{ssb_s}{ssb0_{s,p}}}) -->

<!-- $$ {#eq-obj} -->

<!-- Where *scale* rescales the values to be between 0 and 1 such that the -->

<!-- weight parameter is comparable between vectors. The algorithm works by -->

<!-- first assigning every patch in the system to an MPA. For the first -->

<!-- round, the algorithm then calculates the equilibrium objective function -->

<!-- value resulting from sequentially removing each individual patch from -->

<!-- the MPA network. The cell whose removal from the MPA produces the -->

<!-- highest objective function value is then removed from the MPA network, -->

<!-- and the marginal value of the objective function each of the remaining -->

<!-- cells from the last steps are then stored. For the next steps, we -->

<!-- sampled 25% of the remaining MPA cells with probability proportional to -->

<!-- their marginal contribution to the objective function in the prior -->

<!-- iteration, selecting the cell whose removal produces the highest total -->

<!-- objective function as the cell to remove from the network, and updating -->

<!-- the marginal value of the sampled-but-not-selected cells. This in -->

<!-- essence is a sampling-importance-resampling algorithm. The algorithm -->

<!-- continues until no more cells are left in the MPA. This then provides -->

<!-- for a given objective weighting value $\Phi$ the near-optimal MPA -->

<!-- network at every MPA size from 0 to 100%. We say "near" as they is some -->

<!-- path dependency here, in that for example the network that maximizes the -->

<!-- objective function with 40% of the MPAs does not necessarily contain the -->

<!-- optimal network at 30%. However, the reversed nature of the algorithm, -->

<!-- starting at 100% MPA coverage and working better, produces a more stable -->

<!-- network with regards to this problem than starting at 0% and growing to -->

<!-- 100%. -->

@@

```{r}
#| label: fig-coral-results
#| fig-cap: "Frontier in conservation and yield outcomes under different MPA design strategies (A) for coral reef case study. Change in yield for each fleet (B) and depltion per species (C) as a function of MPA size and MPA design strategy for the coral reef case study."
#| fig-height: 4
#| fig-width: 6

coral_mpa_experiments$mpas <- map(coral_mpa_experiments$results, "mpa")

coral_mpa_experiments$obj <- map(coral_mpa_experiments$results, "obj")

coral_results <- coral_mpa_experiments %>%
  unnest(cols = obj)

@@

In this paper we have documented the core system of equations underlying
`marlin`, and demonstrated how this framework can be used to support
efforts such as MPA planning. The variation in both the magnitude and
distribution of costs and benefits stemming from alternative design
choices and states of nature shown in our results demonstrates the value
in our method. Beyond the current examples, we envision `marlin` being
applicable to research on dynamic ocean management, range shifts,
management strategy evaluation, policy interactions, and spatial stock
assessment. In addition, the process-based movement model used in
`marlin` can directly use empirical estimates of movement dynamics
derived in the manner of @thorson2021a, providing a link between
empirical and simulation based approaches to marine resource management.
Future iterations of the model may include life history modules for a
broader range of species types such as marine mammals, sea birds, and
sea turtles.

### 2022-11-17 README.Rmd
updating makefile instructions

# Something about MPAs and Bycatch

Repo for manuscript exploring the ways in which habitat overlap, fleet spillover, and MPA design strategies can interact to affect conservation and fishery outcomes of MPAs, focused on WCPO-ish system.

>>>>

# Policy Implications of Coupled Economic and Ecological Dynamics in Aquatic Systems

Paper Introducing the `marlin` package.

## Reproducing results on UNIX machines

This repo is equipped with a `make` file. To reproduce results this way

1. Make sure you have make installed

2. Open a terminal and make sure the working directory of the terminal is set to the location of this repo

3. Make sure you have all dependencies installed by opening R and running `renv::restor()`

4. In the terminal, run `RUN_NAME:MyRunName FORMAT:MyFormat make` where MyRunName is the name of the folder you want to create to store results (e.g. v0.1) and FORMAT is one of pdf, html, docx

5. Wait for a bit! This command will run all the required scripts and knit the paper.
